Ultra-deep $K_s$-band Imaging of the \textit{Hubble} Frontier Fields

### 2015-02-20 Paper0/ms.tex
Add cluster redshift to table

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                %
%  Summary table
%                                                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{deluxetable*}{lcclrrcc} 
\tabletypesize{\footnotesize}
\tablewidth{0pt} 
\tablecaption{Field summary \label{tab:summary}} 
\tablehead{ 
\colhead{Field} & \colhead{R.A.} & \colhead{Dec.} & \colhead{Instrument} & \colhead{Epoch} & \colhead{$t$} & \colhead{Depth} & \colhead{FWHM}}
\startdata 
Abell 2744 & 00:14:21.2 & -30:23:50 & \textit{VLT}/HAWKI     & 2013 Oct 24--2013 Dec 24 & 29.4 h & 25.8 & $0\farcs40$ \\ 
MACS-0416  & 04:16:08.9 & -24:04:28 & \textit{VLT}/HAWKI     & 2013 Oct 25--2014 Feb 23 & 25.5 h & 25.9 & $0\farcs38$ \\ 
MACS-0717  & 07:17:34.0 & +37:44:49 & \textit{Keck}/MOSFIRE  & 2015 Jan 26--27                 & \xxx & 25.0 & $0\farcs43$ \\ 
MACS-1149  & 11:49:36.3 & +22:23:58 & \textit{Keck}/MOSFIRE  & 2015 Feb 24                    & \xxx & \xxx & \xxx
\enddata 
%\vspace{-0.8cm} 
\tablecomments{Depth is defined as the 5$\sigma$ limiting magnitude for point sources, measured in $D=0\farcs5$ apertures (\S\ref{s:depth}).} 
\end{deluxetable*}
%\vspace{1cm}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                %
%  Summary table
%                                                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{deluxetable*}{lrcclrrcc} 
\tabletypesize{\footnotesize}
\tablewidth{0pt} 
\tablecaption{Field summary \label{tab:summary}} 
\tablehead{ 
\colhead{Field} & \colhead{$z$} & \colhead{R.A.} & \colhead{Dec.} & \colhead{Instrument} & \colhead{Epoch} & \colhead{$t$} & \colhead{Depth} & \colhead{FWHM}}
\startdata 
Abell 2744 & 0.308 & 00:14:21.2 & -30:23:50 & \textit{VLT}/HAWKI     & 2013 Oct 24--2013 Dec 24 & 29.4 h & 25.8 & $0\farcs40$ \\ 
MACS-0416  & 0.396 & 04:16:08.9 & -24:04:28 & \textit{VLT}/HAWKI     & 2013 Oct 25--2014 Feb 23 & 25.5 h & 25.9 & $0\farcs38$ \\ 
MACS-0717  & 0.545 & 07:17:34.0 & +37:44:49 & \textit{Keck}/MOSFIRE  & 2015 Jan 26--27                 & \xxx & 25.0 & $0\farcs43$ \\ 
MACS-1149  & 0.543 & 11:49:36.3 & +22:23:58 & \textit{Keck}/MOSFIRE  & 2015 Feb 24                    & \xxx & \xxx & \xxx
\enddata 
%\vspace{-0.8cm} 
\tablecomments{Depth is defined as the 5$\sigma$ limiting magnitude for point sources, measured in $D=0\farcs5$ apertures (\S\ref{s:depth}).} 
\end{deluxetable*}
%\vspace{1cm}
